---
title: "regionalOil"
toc: true
format: 
  html:
    embed-resources: true # allows you to click on HTML in order to view
# format:
#   docx:
#     fontsize: 12pt
#     toc: true
#     number-sections: true
bibliography: references.bib
author:
  - name: Rich Ryan
    corresponding: true
    orcid: 0000-0002-6648-5413
    email: richryan@csub.edu
    affiliations:
      - name: California State University, Bakersfield
        address: 9001 Stockdale Highway 
        city: Bakersfield
        state: CA
        postal-code: 93311
  - name: Nyakundi Michieka
    email: nmichieka@csub.edu
    affiliations:
      - name: California State University, Bakersfield
        address: 9001 Stockdale Highway
        city: Bakersfield
        state: CA
        postal-code: 93311        
---

```{r}
#| echo: false
#| include: false # catch-all for removing all output from the code block
source("R/packages.R")
```


# Introduction

This document summarizes the project's contents.
The document serves several purposes:
- Show what the project produces
- Show where someone can locate the material in the code
- In addition to replicating results from the paper, supplemental material is shared.

# Data

## Level of employment measured by the CPS and the QCEW

```{r}
#| echo: false
#| label: fig-empl
#| fig-cap: "Employment"
targets::tar_load(plt_empl)
plt_empl
```

Measured employment in the different counties is shown in figure @fig-empl.
The figure shows employed measured by 
the Current Population Survey and 
the Quarterly Census of Employment and Wages. 

## All counties: Share and level of employment in select 2- and 3-digit NAICS industries

```{r}
#| echo: false
#| label: fig-empl-share-mining-oil-gas
#| fig-cap: "Share of employment in mining and oil and gas extraction"
targets::tar_load(plt_empl_share)
plt_empl_share$plt_all
```

```{r}
#| echo: false
#| label: fig-empl-lvl-mining-oil-gas
#| fig-cap: "Level of employment in mining and oil and gas extraction"
targets::tar_load(plt_empl_ind)
plt_empl_ind
```


## Kern: Share of employment in select 2- and 3-digit NAICS industries

```{r}
#| echo: false
#| label: fig-empl-share-mining-oil-gas-kern
#| fig-cap: "Share of employment in mining and oil and gas extraction"
targets::tar_load(plt_empl_share)
plt_empl_share$plt_kern
```

Figure @fig-empl-share-mining-oil-gas-kern covers the period
`r min(as.Date(layer_scales(plt_empl_share$plt_kern)$x$range$range))` to
`r max(as.Date(layer_scales(plt_empl_share$plt_kern)$x$range$range))`.

# Structural impulse responses

Estimated structural impulse response functions.

## Kern County, California

### All 

```{r}
#| echo: false
#| fig-height: 8
#| fig-width: 7
#| label: fig-svar-kern-paper
#| fig-cap: "Structural impulse response functions in Kern County, California"
targets::tar_load(plt_kern_analysis)
plt_kern_analysis$plt_all 
```

### The oil block

```{r}
#| echo: false
#| fig-height: 8
#| fig-width: 7
#| label: fig-svar-oil-kern
#| fig-cap: "Structural impulse response functions estimated using data from Kern County, California"
targets::tar_load(plt_kern_analysis)
plt_kern_analysis$plt_oil_block
```

### The employment block

```{r}
#| echo: false
#| fig-height: 8
#| fig-width: 7
#| label: fig-svar-empl-kern
#| fig-cap: "Structural impulse response functions estimated using data from Kern County, California"
targets::tar_load(plt_kern_analysis)
plt_kern_analysis$plt_empl_block
```

# Historical decompositions

## Kern County, California

### Check that the historical decomposition can match the level of employment

```{r}
#| echo: false
#| fig-height: 8
#| fig-width: 7
#| label: fig-hd-check-early-kern
#| fig-cap: "Check historical decomposition in Kern County, California, using employment level"
targets::tar_load(dat_hd_lvl_kern_early)
dat_hd_lvl_kern_early$plt_lvl_check
```

Figure @fig-hd-check-early-kern verifies that the historical decomposition can match the level of employment.
The figure covers the period 
`r min(as.Date(layer_scales(dat_hd_lvl_kern_early$plt_lvl_check)$x$range$range))` to
`r max(as.Date(layer_scales(dat_hd_lvl_kern_early$plt_lvl_check)$x$range$range))`.

```{r}
#| echo: false
#| fig-height: 8
#| fig-width: 7
#| label: fig-hd-check-late-kern
#| fig-cap: "Check historical decomposition in Kern County, California, using employment level"
targets::tar_load(dat_hd_lvl_kern_late)
dat_hd_lvl_kern_late$plt_lvl_check
```

Figure @fig-hd-check-late-kern verifies that the historical decomposition can match the level of employment.
The figure covers the period 
`r min(as.Date(layer_scales(dat_hd_lvl_kern_late$plt_lvl_check)$x$range$range))` to
`r max(as.Date(layer_scales(dat_hd_lvl_kern_late$plt_lvl_check)$x$range$range))`.

### Structural factors that explain the growth rate of employment

```{r}
#| echo: false
#| label: fig-hd-components-kern
#| fig-cap: "Structural components that explain the growth rate of employment in Kern County, California"
targets::tar_load(plt_hd_components_kern)
plt_hd_components_kern
```


### Counterfactual employment series

```{r}
#| echo: false
#| fig-height: 8
#| fig-width: 7
#| label: fig-counterfactual-empl-kern-late
#| fig-cap: "Counterfactual employment series in Kern County, California"
targets::tar_load(plt_hd_lvl_kern_early)
targets::tar_load(plt_hd_lvl_kern_late)
plt_hd_lvl_kern_late$plt
```

```{r}
#| echo: false
#| fig-height: 8
#| fig-width: 7
#| label: fig-counterfactual-empl-kern-early
#| fig-cap: "Counterfactual employment series in Kern County, California"
targets::tar_load(plt_hd_lvl_kern)
targets::tar_load(plt_hd_lvl_kern_early)
plt_hd_lvl_kern_early$plt
```

Figure @fig-counterfactual-empl-kern-early shows counterfactual employment series for Kern County, California.
The figure is shown in *levels*. 

The early period begins in 
`r min(pull(plt_hd_lvl_kern_early$df_begin, date))` and goes through
`r min(pull(plt_hd_lvl_kern_early$df_end, date))`.
The later period begins in
`r min(pull(plt_hd_lvl_kern_late$df_begin, date))` and goes through
`r min(pull(plt_hd_lvl_kern_late$df_end, date))`.

Numbers in the chart can be accessed along with what is returned with the chart:
```{r}
cbind(plt_hd_lvl_kern_early$df_begin, plt_hd_lvl_kern_early$df_end)
```

and

```{r}
cbind(plt_hd_lvl_kern_late$df_begin, plt_hd_lvl_kern_late$df_end)
```

# References

::: {#refs}
:::

